Explore spatial allocation

### 2021-02-22 marine/explore_spatial_allocation.Rmd
finished calculating distance to shore for each mariculture practice

source(here::here("_spatial/template_raster.R"))
```

@@

n_farms <- all_farms %>%
  group_by(iso3c, data_quality, group) %>%
  summarise(n_farms = n()) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(avg_quality = mean(data_quality)) %>%
  ungroup()

>>>>

source(here::here("_spatial/template_raster.R"))

gordon_coast <- st_read(file.path("/home/shares/food-systems/Food_footprint/_raw_data/Aquaculture_locations/global_maps/outline_st.shp"))
```

@@

## find average distance to shore per each spp group

## do bivalves 
datalist_biv = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "bivalve")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows) %>%
    filter(row_number > 2322) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_biv[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_biv = do.call(rbind, datalist_biv)

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_biv, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/bivalve_dist.shp"))

## do tunas 
datalist_tuna = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "tuna")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows) #%>%
    #filter(row_number > 2322) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_tuna[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_tuna = do.call(rbind, datalist_tuna)

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_tuna, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/tuna_dist.shp"))

## do marine fish  
datalist_mf = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "marine_fish_general")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows) #%>%
    #filter(row_number > 2322) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_mf[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_mf = do.call(rbind, datalist_mf)

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_mf, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/marine_fish_general_dist.shp"))

## do salmon 
datalist_salmon = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "salmon")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
    mutate(row_number = 1:num_rows)#  %>%
# filter(row_number < 2345, row_number > 2235) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 2235 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_salmon[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

dist_data_salmon = do.call(rbind, datalist_salmon)
## ~100 per hour = there are 3400 rows... = 34 hours to run....

## save the first round just in case... it only made it through 1404 rows. Delete the rows already done and continue
st_write(dist_data_salmon, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/salmon_dist.shp"))

## do shrimp
datalist_shrimp = list()

  group_df <- all_farms_sf %>%
    filter(action_needed == "Land mask") %>%
    filter(group == "shrimp")

  num_rows <- nrow(group_df)

  group_df_final <- group_df %>%
     mutate(row_number = 1:num_rows)
    # filter(row_number > 3464) ## now delete the rows that have already been completed

num_rows_final <- group_df_final$row_number

for(i in num_rows_final){

    # i = 1411 # testing
  final_df <- group_df_final %>%
    filter(row_number == i)

  datalist_shrimp[[i]] <- cbind(final_df, data.frame(distance = st_distance(final_df, gordon_coast)))

}

  dist_data_shrimp = do.call(rbind, datalist_shrimp)

st_write(dist_data_shrimp, file.path("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/point_placement/shrimp_dist.shp"))

## there are no crustaceans that fall in that category
```

```{r}
n_farms <- all_farms %>%
  group_by(iso3c, data_quality, group) %>%
  summarise(n_farms = n()) %>%
  ungroup() %>%
  group_by(iso3c) %>%
  mutate(avg_quality = mean(data_quality)) %>%
  ungroup()
